### 2017-04-14 src/stats6.tex
Converted control chart to tikz picture.

    \subsubsection{Control of means}
        The most common method of statistical process control is to take regular samples and plot them on a control chart as shown in the following diagram:\\
        \includegraphics[scale=0.125]{controlchart}

        \begin{center}
        \begin{tabularx}{\textwidth}{l|X}
        Event & Action \\
        \hline
        Sample mean is between warning limits & No action \\
        Sample mean between warning and action limits & Take another sample immediently, if the new sample mean is outside warning limits take action \\
        Sample mean outside action limits & Take action \\
        \end{tabularx}
        \end{center}

>>>>

    \subsubsection{Control of means}
        The most common method of statistical process control is to take regular samples and plot them on a control chart as shown in the following diagram:\\

        \newcommand{\xpoint}[2]{
            \draw[line width=1] (#1-0.1,#2-0.1) -- (#1+0.1, #2+0.1);
            \draw[line width=1] (#1-0.1,#2+0.1) -- (#1+0.1, #2-0.1);
        }

        \newcommand{\xpointn}[3]{
            \draw[line width=1] (#1-0.1,#2-0.1) -- (#1+0.1, #2+0.1);
            \draw[line width=1] (#1-0.1,#2+0.1) -- (#1+0.1, #2-0.1) node[right]{#3};
        }

        \begin{center}
        \begin{tikzpicture}
        \draw[->, line width=1] (1, 1) -- (1, 5) node[left]{
            \begin{tabular}{r} Sample \\ mean \end{tabular}
        };
        \draw[line width=1] (1, 4.5) -- (10, 4.5) node[right]{Action limit};
        \draw[line width=1] (1, 4) -- (10, 4) node[right]{Warning limit};
        \draw[line width=1] (1, 3) -- (10, 3) node[right]{Target value};
        \draw[line width=1] (1, 2) -- (10, 2) node[right]{Warning limit};
        \draw[line width=1] (1, 1.5) -- (10, 1.5) node[right]{Action limit};
        \xpoint{1.6}{3.2}
        \xpoint{2.4}{2.5}
        \xpoint{3.2}{3.4}
        \xpoint{3.7}{3.7}
        \xpoint{4.1}{3.2}
        \xpoint{4.6}{2.2}
        \xpoint{5.3}{3.1}
        \xpoint{6.1}{3.4}
        \xpoint{6.7}{2.8}

        \xpointn{7.4}{3.8}{(1)}
        \xpointn{7.7}{1.2}{(2)}
        \xpointn{8.7}{4.25}{(3)}
        \end{tikzpicture}
        \end{center}

        \begin{center}
        \begin{tabularx}{\textwidth}{l|X}
        Event & Action \\
        \hline
        (1) Sample mean is between warning limits & No action \\
        (2) Sample mean outside action limits & Take action \\
        (3) Sample mean between warning and action limits & Take another sample immediently, if the new sample mean is outside warning limits take action \\
        \end{tabularx}
        \end{center}
